
% Abstract

\phantomsection
\addcontentsline{toc}{section}{ABSTRACT}
\section*{ABSTRACT}

Stock price and stock index price forecasting system, used by investors and financial managers to describe the market and compare the return on specific investments, has been a topic of research for very long now. When in the stock market, there are more buyers than there are sellers, the price must adapt or no trades are made. This tends to drive the price upwards, increasing the market quotation at which investors can sell their shares, enticing investors who had previously not been interested in selling and vice versa. These demands and supplies are ever changing, resulting in highly-fluctuating, non-linear stock prices which poses a threat against the credibility of those prediction systems which only view the market from one perspective. For a reliable system, it is therefore important to explore the market on multiple grounds. 

The project studies the stock market through Technical, Fundamental and News Sentimental terms and combines various artificial intelligence and data mining techniques in order to predict the stock movements. Under technical analysis, Artificial Neural Networks (ANNs) is employed to analyze the nonlinear relationships between the stock closed price and various technical indexes, and to capture the knowledge of trading signals that are hidden in historical data. The fundamental analysis involves thorough study of financial statements of companies which gives an insight on the company's future performance. Unlike technical analysis, it helps predicting stock price on a long run. In news analysis, we focus on understanding the news sentiment and its affects which may cause the investors to either buy or sell the shares based on positivity or negativity of the news.

Thus, through the circumstantial application of the above-mentioned analysis, the project proposes to predict the stock market in a more generalized manner so that, it can be useful for analysts as well as for general investors for day to day trading. 


\textbf{Keywords : }\textit{Stock Market Prediction, Artificial Neural Network, Technical Analysis, Fundamental Analysis, News-Sentimental Analysis}