
% Acknowledgments

\phantomsection \addcontentsline{toc}{section}{ACKNOWLEDGMENT}
\section*{ACKNOWLEDGMENT}

This project is done as per the requirement of the 4\textsuperscript{th} year
Major Project in Bachelors in Computer Engineering, Institute of Engineering
(IOE), Tribhuvan University, Nepal.

We would like to express our deepest gratitude to Prof. Dr.~Subarna~Shakya for
supervising this project with full dedication, support and guidance. Without
him, this project would have taken twice as long to complete.

We would like to thank the Department of Electronics and Computer
Engineering, IOE for giving us this great opportunity to carry out a major
project that will help us shape our career. Among all the members of the
department, our special thanks goes to the Head of Department,
Dr.~Diwakar~Raj~Pant, and the Deputy Head of Department, Mrs.~Bibha~Sthapit and
Mr.~Dinesh~Baniya~Kshatri, for providing us the support and guidance for this
major project.

We would like to acknowledge all the authors of the research papers that helped
us understand the required concepts and algorithms better, and that we utilized
to prepare this report.

Every attempt has been made to include each and every aspects of the project in
this report so that the reader can clearly understand about our project. We
would be pleased to get the feedback on this project.

~

Sincerely,\\
{\bf Abin~Shakya} (070/BCT/503)\\
{\bf Anuj~Pokhrel} (070/BCT/507)\\
{\bf Ashuta~Bhattarai} (070/BCT/510)\\
{\bf Pinky~Sitikhu} (070/BCT/524)\\
